Geometric variational problems

### 2020-11-11 NSF2020/Description/background.tex
RJR finished background, added refs

\begin{wrapfigure}[14]{l}{0.35\textwidth}
\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:demixing} \footnotesize An initial assembly of
  small and large particles spontaneously segregates into two smaller
  bodies.}
\end{wrapfigure}Over the past decades, researchers have used a number of mathematical
tools to simulate vesicles in a shear flow, including lattice
Boltzmann~\cite{KaouiHartingMisbah2011_PRE}, coarse-grained Brownian
dynamics~\cite{NoguchiTakasu2002_BJ}, phase
field~\cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, level
set~\cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary
integral~\cite{Shravan09,Rahimian15} and immersed boundary
approaches~\cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}.
Most of these approaches assume a mathematical surface, whether
implicitly or explicitly, and define an elastic bending energy of the
surface. Researchers have developed a number of numerical methods for
calculating energy minimizing steady equilibrium shapes of lipid bilayer
membranes, vesicles and red blood cells. These approaches range from the
finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, phase
field method~\cite{Du05,QiangDu08,Lowengrub13} to immersed boundary
method~\cite{Hu,Hu13, KimLai2010_JCP}. PI RR and collaborators led in
part the development of phase field functionals of membrane elastic
energy and approaches to coupling membrane elasticity to
fluids~\cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.

@@

The greatest strength of using HAP to model lipid bilayer membrane is
the ability to form discontinuities (interfacial singularity) from first
physical principles without any artificial manipulation to rearrangement
the interface. For example, using the HAP model to simulate a vesicle
under a shear flow that is strong enough to cause the vesicle membrane
to rupture, we expect the HAP model to capture the reorganization of
lipid molecules on the scales of membrane thickness ($\sim 5$ nm), which
is a nearly impossible task using phase-field or immerse boundary method
without extreme refinement around the membrane and artificial treatment
of reconnection during the topological change of an interface.

>>>>

\begin{wrapfigure}[14]{l}{0.35\textwidth}
\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:demixing} \footnotesize An initial assembly of
  small and large particles spontaneously segregates into two smaller
  bodies.}
\end{wrapfigure}
Over the past decades, researchers have used a number of mathematical
tools to simulate vesicles in a shear flow, including lattice
Boltzmann~\cite{KaouiHartingMisbah2011_PRE}, coarse-grained Brownian
dynamics~\cite{NoguchiTakasu2002_BJ}, phase
field~\cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, level
set~\cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary
integral~\cite{Shravan09,Rahimian15} and immersed boundary
approaches~\cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}.
Most of these approaches assume a mathematical surface, whether
implicitly or explicitly, and define an elastic bending energy of the
surface. Researchers have developed a number of numerical methods for
calculating energy minimizing steady equilibrium shapes of lipid bilayer
membranes, vesicles and red blood cells. These approaches range from the
finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, phase
field method~\cite{Du05,QiangDu08,Lowengrub13} to immersed boundary
method~\cite{Hu,Hu13, KimLai2010_JCP}. PI RR and collaborators led in
part the development of phase field functionals of membrane elastic
energy and approaches to coupling membrane elasticity to
fluids~\cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.

@@

\begin{wrapfigure}[6]{l}{0.35\textwidth}
\centerline{\includegraphics[width=0.35\textwidth]{figures/Lysis.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:lysis} \footnotesize Two hydrophobic particles
  enter and then lyse the circular bilayer.}
\end{wrapfigure}
The greatest strength of using HAP to model lipid bilayer membrane is
the ability to form discontinuities (interfacial singularity) from first
physical principles without any artificial manipulation to rearrangement
the interface (Figures \ref{fig:demixing} and \ref{fig:lysis}).
For example, using the HAP model to simulate a vesicle
under a shear flow that is strong enough to cause the vesicle membrane
to rupture (see \S\ref{sec:preliminary_work}), we expect the HAP model to capture the reorganization of
lipid molecules on the scales of membrane thickness ($\sim 5$ nm), which
is a nearly impossible task using phase-field or immerse boundary method
without extreme refinement around the membrane and artificial treatment
of reconnection during the topological change of an interface
\cite{doi:10.1063/5.0009734,LiAn-Chang16,doi:10.1098/rspa.2012.0505,doi:10.1137/130941432,Feetzl18,doi:10.1137/16M1108406}.
